---
title: "Setup"
output: html_document
date: "2022-10-17"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# electron-quick-start


Update files of electron quick start: 
- `package.json` - Points to the app's main file and lists its details and dependencies.
- `main.js` - Starts the app and creates a browser window to render HTML. This is the app's **main process**.


From your command line:


```{bash}
git clone https://github.com/electron/electron-quick-start

```


```{bash}
# Go into the repository
cd electron-quick-start
# Install dependencies
npm install
```
 
 
```{bash}

cd electron-quick-start
# Run the app
npm start
```


```{r}

curl::curl_download( url = "https://sourceforge.net/projects/rportable/files/R-Portable/4.2.0/R-Portable_4.2.0.paf.exe/download",
                     destfile = "R-Portable_4.2.0.paf.exe")

```
 
 install manually inside the app folder
```{bash}
cd electron-quick-start
open ../R-Portable_4.2.0.paf.exe 
```


```{r}
dir.create( path = "electron-quick-start/renv_cache")

```


`.Renviron`
```
RENV_PATHS_CACHE =  "renv_cache"

```



`.gitignore`
```
.Rproj.user
.Rhistory
.RData
.Ruserdata

```

- add `cc.ico`

`.renvignore`
```{r}
node_modules
R-Portable
renv
renv_cache

```


```{r root.dir = file.path( getwd(), "electron-quick-start") }

# setwd( file.path( getwd(), "electron-quick-start") )

install.packages("renv")
install.packages("usethis")
install.packages("here")

```

app.Rproj
```
Version: 1.0

RestoreWorkspace: No
SaveWorkspace: No
AlwaysSaveHistory: Default

EnableCodeIndexing: Yes
UseSpacesForTab: Yes
NumSpacesForTab: 2
Encoding: UTF-8

RnwWeave: Sweave
LaTeX: pdfLaTeX

AutoAppendNewline: Yes
StripTrailingWhitespace: Yes
LineEndingConversion: Posix

```

## open the app.Rproj

`package.json`

```
{
  "name": "shiny-electron-quick-start",
  "version": "1.0.0",
  "description": "A minimal Electron application with R 4.2.0 and tidyverse and shiny",
  "main": "main.js",
  "scripts": {
    "start": "electron .",
	"package-win": "electron-packager . --overwrite --platform=win32 --arch=ia32 --icon=cc.ico --out=YOElectronShinyAppWindows --version-string.CompanyName=YO --version-string.FileDescription=CE --version-string.ProductName=\"Shiny Electron App\""
  },
  "repository": "https://github.com/electron/electron-quick-start",
  "keywords": [
    "Electron",
    "shiny",
    "R",
    "demo"
  ],
  "author": "laurejo1",
  "license": "MIT",
  "devDependencies": {
    "electron": "^21.1.0"
  }
}


```
 
 
 `main.js`
```

```
 

 
```
cd electron-quick-start

# Run the app
npm start

```

```

cd electron-quick-start
# Compile the app
npm run package-win

```
 

 